---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# airsafety

<!-- badges: start -->
<!-- badges: end -->

The goal of `airsafety` package is to share information about airline safety information with embedded interactive R Shiny application and functions where user can easily calculate rating of an airline based on its safety records.

## Installation

You can install the development version of airsafety from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-jval0011")
```

## How to use `airsafety` package?

Load the `Airsafety` package!

```{r example, warning=FALSE}
library(airsafety)
```

## Functions

```{r echo=FALSE}
library(tibble)
library(kableExtra)

tibble("Function" = c("safetydata", "ratingapp ( )", "airline_rating0 ( )", 
                      "airline_rating ( )"),
       "Description" = c("Access the airline safety data", 
                         "Run the R Shiny application", 
                         "Calculate rating of an airline", 
                         "State rating of an airline")) %>%
  kable() %>%
  kable_styling(full_width = F, 
                bootstrap_options = c("striped", "hover", "condensed"))
```

Note : some functions not mentioned above included in the package are for the embedded R Shiny application purposes. Please refer to the link in section : **"Want to know more about the package?"**

<br>

### `safetydata` : Access the Airline Safety Data

The `airsafety` package includes a built-in dataset `safetydata`, a data frame with **336 rows** and **5 variables**. 

```{r eval=FALSE}
# Access the dataset
airsafety::safetydata
```

Below is a glimpse of the data set:

```{r safetydata, message=FALSE, warning=FALSE}
library(dplyr)
glimpse(safetydata)
```

More details about this dataset can be found by using the function `help(safetydata)`

<br>

### `rating_app()` : Run the R Shiny Application

To run the R shiny application, with the following code:

```{r ratingapp, eval = FALSE}
rating_app()
```

More information about how to use the app can be found at the **about** section of the application.

<br>

### `airline_rating0()`& `airline_rating()` : Check Rating of An Airline

Without running the Shiny Application, you can also check the rating of the airlines using the functions in the `airsafety` package. *Please note only the 56 airlines listed in the built-in data set* `safetydata` *are rated for the airline safety.*

- `airline_rating0()` : calculate the rating

```{r airrate0}
airline_rating0("Qantas")
```
For more details : `help(airline_rating0)`

<br>

- `airline_rating()` : state the rating in sentence

```{r airrate}
airline_rating("Qantas")
```
For more details : `help(airline_rating)`

<br>

## Want to know more about the package?

Visit the `airsafety` [pkgdown website](https://etc5523-2022.github.io/rpkg-jval0011/) for more information on the functions in this package.
