---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tibble)
library(kableExtra)
```

# airsafety

<!-- badges: start -->
<!-- badges: end -->

The goal of `airsafety` package is to share information about airline safety information with embedded interactive R Shiny application and functions where user can easily calculate rating of an airline based on its safety records.

## Installation

You can install the development version of airsafety from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-jval0011")
```

## How to use `airsafety` package?

Load the `Airsafety` package!

```{r example}
library(airsafety)
```

## Functions

```{r}
tibble("Function" = c("safetydata", "ratingapp()", "airline_rating0()", 
                      "airline_rating()"),
       "Description" = c("Access the airline safety data", 
                         "Run the R Shiny application", 
                         "Calculate rating of an airline", 
                         "State rating of an airline")) %>%
  kable() %>%
  kable_styling(full_width = F, 
                bootstrap_options = c("striped", "hover", "condensed"))
```

Note : some functions not mentioned above included in the package are for the embedded R Shiny application purposes. Please refer to the section **"Want to know more about the package?"**

## Want to know more about the package?

Visit the `airsafety` [pkgdown website]() or the for more information on the functions in this package.
