---
title: "Introduction to Airsafety Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Airsafety Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# What is `airsafety` package?

`Airsafety` package contains the airline safety data, functions and includes a Shiny Application for user to interactively learn more about safety of airlines around the world.

This vignette will show you how to access the app and check the rating of the airlines using the `airsafety` package.


## How to use `airsafety` package?

First, load/download the `Airsafety` package!

```{r setup, message=FALSE, warning=FALSE}
# devtools::install_github("etc5523-2022/rpkg-jval0011")
library(airsafety)
```

Next you can access the airline safety data, shiny app and the rating functions with the following steps:

### Access the Airline Safety Data

The `airsafety` package includes a built-in dataset `safetydata`, a data frame with **336 rows** and **5 variables**. Below is a glimpse of the data set:

```{r eval=FALSE}
airsafety::safetydata
```

```{r safetydata, message=FALSE, warning=FALSE}
library(dplyr)
glimpse(safetydata)
```

More details about this dataset can be found by using the function `help(safetydata)`

### Run the R Shiny Application

To run the R shiny application, with the following code:

```{r ratingapp, eval = FALSE}
rating_app()
```

More information about how to use the app can be found at the **about** section of the application.

### Check Rating of An Airline

Without running the Shiny Application, you can also check the rating of the airlines using the functions in the `airsafety` package. *Please note only the 56 airlines listed in the built-in data set* `safetydata` *are rated for the airline safety.*

- `airline_rating0()` : calculate the rating

```{r airrate0}
airline_rating0("Qantas")
```
For more details : `help(airline_rating0)`

<br>

- `airline_rating()` : state the rating in sentence

```{r airrate}
airline_rating("Qantas")
```
For more details : `help(airline_rating)`

## Further Information

For more information about the functions mentioned above and the functions use in the Shiny Application included in the `airsafety` package, please refer to the [pkgdown](https://etc5523-2022.github.io/rpkg-jval0011/) site.

